Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-17 paper/lostanlenRelevanceScattering.tex
covariant -> equivariant

The situation is different in the time-frequency domain. If the wavelet
$\boldsymbol{\psi}(t)$ has a symmetric envelope, that is, if there
exists a phase shift $\varphi\in[0;2\pi[$ such that $\boldsymbol{\psi}(-t)=\mathrm{e}^{\mathrm{i}\varphi}\boldsymbol{\psi}(t)$,
the wavelet transform is covariant with respect to time reversal:
\begin{eqnarray*}
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma) & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\int_{-\infty}^{+\infty}\boldsymbol{x}(-t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(t^{\prime}-t)\;\mathrm{d}t^{\prime}\right|\\
 & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\right|\times\left|\int_{-\infty}^{+\infty}\boldsymbol{x}(t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(-t-t^{\prime})\;\mathrm{d}t^{\prime}\right|\\
 & = & \mathbf{U}_{1}\boldsymbol{x}(t,\gamma).
\end{eqnarray*}
Gabor wavelets have a symmetric envelope, as they satisfy $\boldsymbol{\psi}(-t)=-\boldsymbol{\psi}(t)$,
i.e. $\varphi=\pi$. This is due to the fact that Gaussians have bell-shaped
symmetric envelopes. Therefore, the Gabor wavelet transform commutes
with time reversal: 
\[
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma)=\mathbf{U}_{1}\boldsymbol{x}(-t,\gamma).
\]
A simple way to break this undesirable invariance is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.

>>>>

The situation is different in the time-frequency domain. If the wavelet
$\boldsymbol{\psi}(t)$ has a symmetric envelope, that is, if there
exists a phase shift $\varphi\in[0;2\pi[$ such that $\boldsymbol{\psi}(-t)=\mathrm{e}^{\mathrm{i}\varphi}\boldsymbol{\psi}(t)$,
the wavelet transform is equivariant with respect to time reversal:
\begin{eqnarray*}
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma) & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\int_{-\infty}^{+\infty}\boldsymbol{x}(-t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(t^{\prime}-t)\;\mathrm{d}t^{\prime}\right|\\
 & = & \left|\mathrm{e}^{\mathrm{i}\varphi}\right|\times\left|\int_{-\infty}^{+\infty}\boldsymbol{x}(t^{\prime})\boldsymbol{\psi}_{2^{\gamma},T(2^{\gamma})}(-t-t^{\prime})\;\mathrm{d}t^{\prime}\right|\\
 & = & \mathbf{U}_{1}\boldsymbol{x}(t,\gamma).
\end{eqnarray*}
Gabor wavelets have a symmetric envelope, as they satisfy $\boldsymbol{\psi}(-t)=-\boldsymbol{\psi}(t)$,
i.e. $\varphi=\pi$. This is due to the fact that Gaussians have bell-shaped
symmetric envelopes. Therefore, the Gabor wavelet transform commutes
with time reversal: 
\[
\mathbf{U}_{1}(\mathcal{W}_{\boldsymbol{\tau}}\boldsymbol{x})(t,\gamma)=\mathbf{U}_{1}\boldsymbol{x}(-t,\gamma).
\]
A simple way to break this undesirable invariance is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.
